### 2022-01-18 documentos/math.tex
This should work until december 2013.

The same program can be carried out for $N$ qubits. In this case, 
the vectorized Pauli operators are 
\begin{align}
\kket{\sigma_{\vec{\alpha} }}&=\kket{\sigma_{\alpha_1}}\otimes\cdots
\otimes\kket{\sigma_{\alpha_N}} \nonumber \\
&=\kket{\sigma_{\alpha_1}\otimes\cdots
\otimes\sigma_{\alpha_N}},
\end{align}
\ddnote{Recordatorio de que esta igualdad esta mal, si solo se necesita la vectorizacion de la Pauli string, con eso.}
% 
% $\janote{aquí hay algo extraño, pues los operadores 
% que utilizamos son la vectorización del producto tensorial de las paulis, no los
% productos tensoriales de las paulis vectorizadas, que es lo que entiendo con la 
% expresión $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\cdots
% \otimes\kket{\sigma_{\alpha_N}}$}\janote{mi sugerencia es nada más reescribir
% $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}\otimes\cdots
% \otimes\sigma_{\alpha_N}}$}
% kkkj
and satisfy the orthogonality relation
$\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} =  2^N
\delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of the
map corresponding to a Pauli diagonal operation is 
% Analogously to the single qubit case, one can define the $N$-qubits Pauli map $\mathcal{E}_N$
% % 
% \begin{equation}
% \rho \to \rho'=\mathcal{E}_N[\rho ]=\frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
% % \label{Pauli_Map}
% \end{equation}
% % 
% with $-1\leq \tau_{\vec{\alpha}} \leq 1$. 
% % 
% In this case the density matrix in vector form holds 
% % 
% \begin{equation}
%  \kket{\rho}=\frac{1}{2^N}\sum_{\vec{\alpha}} r_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
% \end{equation}
% where $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\dots
% \otimes\kket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation
% $\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} = \tr
% \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N
% ~\delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of this map is
% given by
\begin{equation}
\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} \ddyada{\sigma_{\vec{\alpha} }}.
\end{equation}
As in the previous case, the Choi matrix $\mathcal{D}_N$ may be written in
terms of tensor products of Pauli matrices
\begin{equation}
 \mathcal{D}_N 
  = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}}
       \bigotimes_{j=1}^N \sigma_{\alpha_j} \otimes \sigma_{\alpha_j}^*.
%  \label{Choi_1}
\end{equation}
This superoperator is again diagonal in the (multi-qubit) Pauli basis, with the 
eigenvalue corresponding to 
$ \kket{\sigma_{\vec{\alpha} }}$ given by 
% 
% After several steps, it is possible to prove that analogously to the single qubit case, $\mathcal{D}_N$ is diagonal in the $N$-qubits Pauli basis
% \begin{equation}
%  \mathcal{D}_N \kket{\sigma_{\vec{\alpha} }}
%    = \lambda_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
% \end{equation}
% with eigenvalues $\lambda_{\vec{\alpha}}$ given by 
\begin{equation}
 \lambda_{\valpha} = \frac{1}{2^N} \sum_{\vbeta} \san_{\valpha\vbeta}\tau_{\vbeta},
\label{eq:lambda:is:A:tau}
\end{equation}
where 
\begin{equation}\label{eq:san}
 \san=\sa^{\otimes N}
% =\frac{1}{2^N}\left(H\otimes H\right)^{\otimes N}=\left(\frac{H}{\sqrt{2}}\right)^{\otimes 2N}.
\end{equation}
Again, the proofs are provided in appendix \ref{sec:appendix:diagonalization}. We wish 
to add that we could diagonalize $\mathcal{D}_N$ with $H^{\otimes 2N}$ instead of
$a^N$, which might be more convenient for other applications.\janote{en una 
iteración posterior del artículo completo quizás es buena idea enmarcar más esto
último de la otra a, ya que puede ser de interés en alguna aplicación}
% \cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar para $N$ 
% qubits.}
% (Proofs in an appendix using binary indices XD)
% }}}

>>>>

The same program can be carried out for $N$ qubits. In this case, 
the vectorized Pauli operators are 
\begin{align}
\kket{\sigma_{\vec{\alpha} }}&=\kket{\sigma_{\alpha_1}}\otimes\cdots
\otimes\kket{\sigma_{\alpha_N}} 
\nonumber \\
&=\kket{\sigma_{\alpha_1}\otimes\cdots
\otimes\sigma_{\alpha_N}},
\end{align}
\ddnote{Recordatorio de que esta igualdad esta mal, si solo se necesita la
vectorizacion de la Pauli string, con eso.}
% 
% $\janote{aquí hay algo extraño, pues los operadores 
% que utilizamos son la vectorización del producto tensorial de las paulis, no los
% productos tensoriales de las paulis vectorizadas, que es lo que entiendo con la 
% expresión $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\cdots
% \otimes\kket{\sigma_{\alpha_N}}$}\janote{mi sugerencia es nada más reescribir
% $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}\otimes\cdots
% \otimes\sigma_{\alpha_N}}$}
% kkkj
and satisfy the orthogonality relation
$\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} =  2^N
\delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of the
map corresponding to a Pauli diagonal operation is 
% Analogously to the single qubit case, one can define the $N$-qubits Pauli map $\mathcal{E}_N$
% % 
% \begin{equation}
% \rho \to \rho'=\mathcal{E}_N[\rho ]=\frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
% % \label{Pauli_Map}
% \end{equation}
% % 
% with $-1\leq \tau_{\vec{\alpha}} \leq 1$. 
% % 
% In this case the density matrix in vector form holds 
% % 
% \begin{equation}
%  \kket{\rho}=\frac{1}{2^N}\sum_{\vec{\alpha}} r_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
% \end{equation}
% where $\kket{\sigma_{\vec{\alpha} }}=\kket{\sigma_{\alpha_1}}\otimes\dots
% \otimes\kket{\sigma_{\alpha_N}}$, and satisfy the usual orthogonality relation
% $\bbrakket{{\sigma_{\vec{\alpha} } }}{{\sigma_{\vec{\alpha}'} }} = \tr
% \left(\sigma_{\vec{\alpha}}^{\dagger} \sigma_{\vec{\alpha}'}\right) = 2^N
% ~\delta_{\vec{\alpha}\vec{\alpha}'}$. The matrix representation of this map is
% given by
\begin{equation}
\hat{\mathcal{E}}_N = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}} \ddyada{\sigma_{\vec{\alpha} }}.
\end{equation}
As in the previous case, the Choi matrix $\mathcal{D}_N$ may be written in
terms of tensor products of Pauli matrices
\begin{equation}
 \mathcal{D}_N 
  = \frac{1}{2^N}\sum_{\vec{\alpha}} \tau_{\vec{\alpha}}
       \bigotimes_{j=1}^N \sigma_{\alpha_j} \otimes \sigma_{\alpha_j}^*.
%  \label{Choi_1}
\end{equation}
This superoperator is again diagonal in the (multi-qubit) Pauli basis, with the 
eigenvalue corresponding to 
$ \kket{\sigma_{\vec{\alpha} }}$ given by 
% 
% After several steps, it is possible to prove that analogously to the single qubit case, $\mathcal{D}_N$ is diagonal in the $N$-qubits Pauli basis
% \begin{equation}
%  \mathcal{D}_N \kket{\sigma_{\vec{\alpha} }}
%    = \lambda_{\vec{\alpha}} \kket{\sigma_{\vec{\alpha} }},
% \end{equation}
% with eigenvalues $\lambda_{\vec{\alpha}}$ given by 
\begin{equation}
 \lambda_{\valpha} = \frac{1}{2^N} \sum_{\vbeta} \san_{\valpha\vbeta}\tau_{\vbeta},
\label{eq:lambda:is:A:tau}
\end{equation}
where 
\begin{equation}\label{eq:san}
 \san=\sa^{\otimes N}
% =\frac{1}{2^N}\left(H\otimes H\right)^{\otimes N}=\left(\frac{H}{\sqrt{2}}\right)^{\otimes 2N}.
\end{equation}
Again, the proofs are provided in appendix \ref{sec:appendix:diagonalization}. We wish 
to add that we could diagonalize $\mathcal{D}_N$ with $H^{\otimes 2N}$ instead of
$a^N$, which might be more convenient for other applications.
% \janote{en una 
% iteración posterior del artículo completo quizás es buena idea enmarcar más esto
% último de la otra a, ya que puede ser de interés en alguna aplicación}
% \cpnote{Mencionar que con la otra $a$ tambien se puede diagonalizar para $N$ 
% qubits.}
% (Proofs in an appendix using binary indices XD)
% }}}
